---
title: "A Collection of Different Functions to Display ASAP Simulation Results"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    fig_caption: yes
    fig_height: 8
    fig_width: 10
    highlight: pygments
    theme: spacelab
    toc: yes
    toc_depth: 6
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '6'
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}

library(writexl)
knitr::opts_chunk$set( echo = TRUE )
```

# Set up

```{r source previous script,  include=FALSE}
# Load script 08
source(here::here("simulation_pipeline/08_run_simulation.R"))
```

```{r run read_and_aggregate}
#NC 12-2-24: this code is now in  a separate combining script, just loading the file now
#combined_all = read.xlsx(here::here("graphs/combined/combined_all.xlsx"))
combined_all = read.xlsx(here::here("graphs/combined/master_aggregated_CATE.xlsx"))

```

```{r specify axis maximums by simulation run and create euclidean_distance}

  #specifying axis maximums (x and y both) and breaks by datasets
  #update this when adding new datasets/outcomes
  #TODO: may need to change these depending on future simulation results
  scenario_maximums = rbind(
    data.frame(dataset = "asap", outcome = "X16BTMCRET", max = 1.2, max_bias = 1.2, max_se = 1.2, breaks = I(list(c(0,.2,.4,.6,.8, 1))),max_agg = .35, max_bias_agg = .35, max_se_agg = .35, breaks_agg = I(list(c(0,.1,.2,.3)))),
    data.frame(dataset = "asap", outcome = "C16BMVDEG", max = 1, max_bias = 1, max_se = 1, breaks = I(list(c(0,.2,.4,.6,.8))),max_agg = 1, max_bias_agg = 1, max_se_agg = 1, breaks_agg = I(list(c(0,.2,.4,.6,.8)))))

```

```{r define df and shape maps}

all_scenarios = combined_all
df = combined_all
all_scenarios$set_id = paste( df$dataset, df$outcome, df$cov_set_size, df$train_set_size, sep="-" )

ALL_MODELS <- unique( all_scenarios$model )

TYPE_SHAPE_MAP <- c(
  "ATE" = 20, "OLS S" = 18, 
  "INF" = 2, "RF" = 3, "CDML" = 8,
  "LASSO" = 10, "SL" = 16,
  "XGBOOST" = 1, "BART" = 0
)

TYPE_COLOR_MAP <- c(
  "ATE" = "black", "OLS S" = "black", 
  "INF" = "darkgrey", "RF" = "#E69F00", "CDML" = "#F0E442",
  "LASSO" = "#009E73", "SL" = "#D55E00",
  "XGBOOST" = "#CC79A7", "BART" = "#0072B2" # "#56B4E9"
)
LEGEND_COLORS = setdiff( names(TYPE_COLOR_MAP), c("LASSO INF", "RF INF", "ATE", "OLS S") )

# For individual methods
SHAPE_MAP <- c(
  "ATE" = 0, "OLS S" = 1, 
  "RF INF" = 2, "RF T" = 3, "RF MOM IPW" = 4, "RF MOM DR" = 5, 
  "CF" = 6, "CF LC" = 7, "CDML" = 8, "LASSO INF" = 9, "LASSO T" = 10, "LASSO MOM IPW" = 11, 
  "LASSO MOM DR" = 12, "LASSO MCM" = 13, "LASSO MCM EA" = 14, "LASSO R" = 15, 
  "SL T" = 16, "SL S" = 17, "XGBOOST S" = 18, "XGBOOST R" = 19, "BART T" = 20, "BART S" = 21
)

old_type_shape_map <- c(
  "ATE" = 18, "OLS S" = 20, "INF" = 2, "RF" = 3, "CDML" = 8,  "LASSO" = 10, "SL" = 16, "XGBOOST" = 0, "BART" = 1
)
old_shape_map <- c(
  "ATE" = 0, "OLS S" = 1, "RF INF" = 2, "RF T" = 3, "RF MOM IPW" = 4, "RF MOM DR" = 5, 
  "CF" = 6, "CF LC" = 7, "CDML" = 8, "LASSO INF" = 9, "LASSO T" = 10, "LASSO MOM IPW" = 11, 
  "LASSO MOM DR" = 12, "LASSO MCM" = 13, "LASSO MCM EA" = 14, "LASSO R" = 15, 
  "SL T" = 16, "SL S" = 17, "XGBOOST S" = 18, "XGBOOST R" = 19, "BART T" = 20, "BART S" = 21
)


```





```{r aggregate to all_scenarios_agg excl ATE, include=FALSE}
# Mean of all queens that are already aggregated excluding ATE
all_scenarios_agg = all_scenarios %>%
                filter(!(queen %in% c("ATE")), ,
                       !(model %in% c("SL S", "SL T", "XGBOOST S", "XGBOOST R"))) %>% 
                group_by(set_id, dataset, outcome, cov_set_size, train_set_size,
            model, type, modelshort) %>%
                summarise(bias = mean(bias),
                          SE = mean(se),
                          RMSE = mean(rmse),
                          percent_cut = mean(percent_cut),
                          runtime = mean(runtime),
                          .groups = "drop")

all_scenarios_agg$se = all_scenarios_agg$SE
# Update naming and tags for clarity and shorter names ----
# Keep ATE and OLS as baseline, and drop labels for the baseline models
all_scenarios_agg <- mutate( all_scenarios_agg,
                  baseline = model %in% c( "ATE", "OLS S", "LASSO INF", "RF INF" ),
                  modelshort = ifelse( baseline, "", modelshort ) )
all_scenarios_agg$modelshort <- str_replace( all_scenarios_agg$modelshort, "MOM ", "" )
all_scenarios_agg$modelshort <- str_replace( all_scenarios_agg$modelshort, "CF LC", "CF-LC" )
all_scenarios_agg$modelshort <- str_replace( all_scenarios_agg$modelshort, "MCM EA", "EA" )

table( all_scenarios_agg$modelshort )

```

# Figures 

## An example of each kind of visualization

## contour_onequeen (shown: asap_1_small_1000 for RF T queen)

```{r example contour_onequeen}
contour_onequeen(scen_dataset="asap", scen_outcome = "X16BTMCRET", scen_train_set_size = "1000", scen_cov_set_size = "small", plotqueen = "RF T")

```

## scenario_plot (shown: asap_2_small_1000)

```{r run scenario_plot 1}
scenario_plot(scen_dataset="asap", scen_outcome = "X16BTMCRET", scen_train_set_size = "1000", scen_cov_set_size = "small")
```

## Stacked mini plots for ASAP outcome 2

```{r stack miniplots}

stack_miniplots(scen_dataset= "asap", scen_outcome = "X16BTMCRET"
               # , scen_train_set_size = "2000", scen_cov_set_size = "small"
                )
```
## ATE and CDML queens only

```{r ATE/CDML queen plots}
plot_two_queens(scen_dataset= "asap", scen_outcome = "X16BTMCRET", queen1="ATE", queen2="CDML")

```

## continuous scenario_allqueens (shown: asap_2_small_1000)


```{r exampl scenario_allqueens asap outcome 2}
scenario_allqueens(scen_dataset="asap", scen_outcome = "X16BTMCRET", scen_train_set_size = "1000", scen_cov_set_size = "small")
```
## TODO: fix binary scenario_allqueens (shown: asap_1_small_1000) 

```{r exampl scenario_allqueens 1}
scenario_allqueens(scen_dataset="asap", scen_outcome = "C16BMVDEG", scen_train_set_size = "2000", scen_cov_set_size = "small")
```

## All queens, by estimator (note: CDML is off the chart to the right at 1)


```{r bias boxplot}

scenario_boxplot(scen_dataset="asap", scen_outcome = "X16BTMCRET", scen_train_set_size = "1000", scen_cov_set_size = "small", metric = "bias")

```

## Percent poorly estimated

```{r percent poorly estimated}

scenario_poorlyest(scen_dataset="asap", scen_outcome = "X16BTMCRET", scen_train_set_size = "1000", scen_cov_set_size = "small")

```

## Trail plot


```{r trail plot}

# Moving to large covariate set plot  ----


scenario_trail(scen_dataset="asap", scen_outcome = "X16BTMCRET", 
                   additional_filter_var = "cov_set_size",
                   additional_filter_val = "small", 
                   trail_var = "train_set_size",
                   trail_val_from = 1000, 
                   trail_val_to = 5000)

```


## Regression Plots

### Coefficient Plot

```{r coef_plot}
cs = make_cs(all_scenarios,scen_dataset = "ca", scen_outcome="Y18JBERNA_06")
coef_plot(cs)

```


### Coefficient Plot, Model Only

```{r coef_plot 2}
cs = make_cs(all_scenarios,scen_dataset = "ca", scen_outcome="Y18JBERNA_06")
coef_plot(cs, plotOnly = "model")

```

### Ex Factor Plot, CA outcome 1
```{r ex_factor_plot}

c_coef = make_c_coef(all_scenarios, scen_dataset = "ca", scen_outcome="Y18JBERNA_06" )
ex_factor_plot(c_coef)

```


## TO DO: not added yet
### Animations
### Others?

