---
title: "Combined Results Template - Work in Progress"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    fig_caption: yes
    fig_height: 8
    fig_width: 10
    highlight: pygments
    theme: spacelab
    toc: yes
    toc_depth: 6
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '6'
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
library(writexl)
knitr::opts_chunk$set(echo = TRUE)
```

# Exact call used to run the simulation

Simulation parameters: CA, continuous outcome (AVG MONTHLY EARNINGS IN 2006 DOLLARS), train set of 1000, small covariate set, with sigma 0.2, with proportion treated set to proportion in real data. All models except SL, all queens including SL, 100 iters. Parallel.

```{r eval=FALSE}
ca_simulation <- run_simulation(
                                # Required arguments
                                real_data = ca_subset_imputed, 
                                realdata_file_path = NULL,
                                dataset_name = "ca",    
                                covariates = ca_small_set,
                                outcome = "Y18JBERNA_06",
                                treatment = ca_treatment,
                                
                                # Optional arguments
                                large_covariate_set = ca_large_set, 
                                small_covariate_set = ca_small_set, 
                                all_outcomes = ca_outcomes,
                                S = 100,  
                                queen_list = DEFAULT_QUEEN_LIST,
                                p_tx = NULL,
                                size_train = 1000,
                                size_test = 10000, 
                                PARALLEL = TRUE,
                                verbose = 1000,
                                include_LASSO = TRUE,
                                include_RF = TRUE,
                                include_SL_S = FALSE,
                                include_SL_T = FALSE,
                                include_CDML = TRUE,
                                include_XGBOOST = TRUE,
                                include_BART = TRUE,
                                master_seed = NULL,
                                baseline_seed = 68814, 
                                baseline_N = 100000, 
                                baseline_directory_path =  here::here("baseline"),
                                true_iates_directory_path = here::here("true_iates"),
                                today = Sys.Date() 
                                )
```

# Set up

```{r source previous script,  include=FALSE}
# Load script 09
source(here::here("simulation_pipeline/09_combine_results.R"))
```

#Specify axis maximums, shape maps, etc

```{r specify axis maximums by simulation run and create euclidean_distance}

  #specifying axis maximums (x and y both) and breaks by datasets
  #update this when adding new datasets/outcomes
  scenario_maximums = rbind(
    #ca outcome 1 (continuous)
    data.frame(dataset = "ca",
               outcome_index = "1", 
               max = .350, 
               breaks = I(list(c(0,.050,.100,.150,.200,.250)))),
    
    #ca outcome 2 (binary)
    data.frame(dataset = "ca", 
               outcome_index = "2", 
               max = .15, 
               breaks = I(list(c(0,.05,.10)))),
  
    #asap outcome 2 (continuous)
    data.frame(dataset = "asap", 
               outcome_index = "2", 
               max = .25, 
               breaks=I(list(c(0,.05,.10,.15,.20)))))


# Function to make RMSE contour plots ----

TYPE_SHAPE_MAP <- c(
  "ATE" = 20, "OLS S" = 18, 
  "INF" = 2, "RF" = 3, "CDML" = 8,
  "LASSO" = 10, "SL" = 16,
  "XGBOOST" = 1, "BART" = 0
)

TYPE_COLOR_MAP <- c(
  "ATE" = "black", 
  "OLS S" = "black", 
  "INF" = "darkgrey", 
  "RF" = "#E69F00", 
  "CDML" = "#F0E442",
  "LASSO" = "#009E73", 
  "SL" = "#D55E00",
  "XGBOOST" = "#CC79A7", 
  "BART" = "#0072B2" # "#56B4E9"
)
LEGEND_COLORS = setdiff(names(TYPE_COLOR_MAP), c("LASSO INF", "RF INF", "ATE", "OLS S"))

# For individual methods
SHAPE_MAP <- c(
  "ATE" = 0, 
  "OLS S" = 1, 
  "RF INF" = 2, 
  "RF T" = 3, 
  "RF MOM IPW" = 4, 
  "RF MOM DR" = 5, 
  "CF" = 6, 
  "CF LC" = 7, 
  "CDML" = 8, 
  "LASSO INF" = 9, 
  "LASSO T" = 10, 
  "LASSO MOM IPW" = 11, 
  "LASSO MOM DR" = 12, 
  "LASSO MCM" = 13, 
  "LASSO MCM EA" = 14, 
  "LASSO R" = 15, 
  "SL T" = 16, 
  "SL S" = 17, 
  "XGBOOST S" = 18, 
  "XGBOOST R" = 19, 
  "BART T" = 20, 
  "BART S" = 21
)

```

```{r read in combined_all, aggregate across queens excluding ATE}

df = combined_all
df$set_id = paste(df$dataset, 
                  df$outcome_index, 
                  df$cov_set_size, 
                  df$train_set_size, sep="-")

ALL_MODELS <- unique(df$model)

no_core <- function(df_set) {
  df_set %>% filter(!baseline)
}
only_core <- function(df_set) {
  df_set %>% filter(baseline)
}


# Mean of all queens that are already aggregated excluding ATE
df_agg = df %>%
                filter(queen != "ATE") %>% 
                group_by(set_id, dataset, outcome_index, 
                         cov_set_size, train_set_size,
                         model, type, modelshort) %>%
                summarise(bias = mean(bias),
                          SE = mean(se),
                          RMSE = mean(rmse),
                          .groups = "drop")

# Update naming and tags for clarity and shorter names ----

# Keep ATE and OLS as baseline, and drop labels for the baseline models
baseline_models = c("ATE", "OLS S", "LASSO INF", "RF INF")
df_agg <- mutate(df_agg,
                  baseline = model %in% baseline_models,
                  modelshort = ifelse(baseline, "", modelshort))

table(df_agg$modelshort)

df_agg$modelshort <- str_replace(df_agg$modelshort, "MOM ", "")
df_agg$modelshort <- str_replace(df_agg$modelshort, "CF LC", "CF-LC")
df_agg$modelshort <- str_replace(df_agg$modelshort, "MCM EA", "EA")

table(df_agg$modelshort)
```


```{r create contour_plot_base function, include=FALSE}
#TODO: document contour_plot_base function, move to separate file?
contour_plot_base <- function(max_bias ,
                               max_se ,
                               breaks) {
  
  euclidean_distance = make_euclidean_distance(max_bias, max_se)
  
  plot_base <- list(
    geom_contour(
      data = euclidean_distance,
      aes(x = x, y = y, z = z),
      breaks = breaks 
),
    theme_minimal(),
    theme(
      plot.background = element_rect(fill = "white", color = NA),
      panel.background = element_rect(fill = "white", color = NA),
      text = element_text(color = "black"),
      plot.title = element_text(size = 16),
      plot.subtitle = element_text(size = 12),
      axis.title = element_text(size = 14),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 12)
),
    labs(
      title = "Bias and SE, averaged across Queens",
      subtitle = "* ATE queen is excluded",
      col = "Model Type",
      y = "Bias",     # Change X-axis title
      x = "SE"),     # Change Y-axis title
    scale_shape_manual(values = TYPE_SHAPE_MAP),
    scale_color_manual(values = TYPE_COLOR_MAP, breaks = LEGEND_COLORS),
    guides(color = guide_legend(title = "Model Type"),
           shape = guide_legend(title = "Model Type")),
    coord_fixed()
)
  plot_base
}

```


```{r create make_contour_plot function, include=FALSE}

make_contour_plot <- function(df_set,
                               max_bias ,
                               max_se ,
                               breaks,
                               add_labels = TRUE) {
  
  p <- ggplot(df_set, aes(se, bias, xmax=max_se, ymax=max_bias)) +
    geom_point(aes(color = type, shape = type),  size = 4) + 
    contour_plot_base(max_bias = max_bias, max_se = max_se , breaks= breaks)
  
  if (add_labels) {
    p <- p +
      ggrepel::geom_label_repel(
        aes(label = modelshort, col = type),
        size = 3, # Increased label size
        box.padding = 0.75,
        point.padding = 0.25,
        max.overlaps = Inf,
        show.legend = FALSE
)
    
  }
  
  p
}

```


```{r create scenario_plot function, include=FALSE}
#make a plot for a given scenario 
#TODO: add documentation

scenario_plot = function(scen_dataset, scen_outcome_index, scen_train_set_size, scen_cov_set_size){
  
  usedata = df_agg %>%
  filter(dataset ==scen_dataset)%>%
  filter(outcome_index ==scen_outcome_index)%>%
  filter(cov_set_size ==scen_cov_set_size)%>%
  filter(train_set_size ==scen_train_set_size)
  
  scen_max = scenario_maximums%>%filter(dataset == scen_dataset & outcome_index == scen_outcome_index)%>% select(max) %>% unlist()
  max_bias = scen_max
  max_se = scen_max
  breaks = unlist(scenario_maximums%>%filter(dataset == scen_dataset & outcome_index == scen_outcome_index)%>% select(breaks))

  #use scen_max to create euclidean_distance
  euclidean_distance=make_euclidean_distance(scen_max,scen_max)

#create the plot itself
p <- ggplot(usedata, aes(SE, bias, xmax=scen_max, ymax=scen_max)) +
  geom_contour(
    data = euclidean_distance,
    aes(x = x, y = y, z = z),
    breaks = c(breaks),
    alpha = 0.6
) +
  geom_point(aes(color = type, shape=type),  size = 4) +
  geom_label_repel(
    aes(label = modelshort, col = type),
    size = 3, # Increased label size
    box.padding = 0.75,
    point.padding = 0.25,
    max.overlaps = Inf,
    show.legend = FALSE
) +
  scale_x_continuous(limits=c(0,scen_max))+
  theme_minimal() +
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    text = element_text(color = "black"),
    plot.title = element_text(size = 16),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12)
) +
  labs(
    title = "Mean of Aggregated Bias and SE across Queens\nfor Each Algorithm with RMSE Contouring",
    subtitle = "* ATE queen is excluded",
    col = "Model Type"
) +
  ylab("Bias") +    # Change X-axis title
  xlab("SE")  +     # Change Y-axis title
  scale_shape_manual(values = TYPE_SHAPE_MAP) +
  guides(color = guide_legend(title = "Model Type"),
         shape = guide_legend(title = "Model Type"))

  print(p)
  
gbs = filter(usedata, model %in% c("ATE", "OLS S", "LASSO INF", "RF INF"))
gbs$model

p1C <- ggplot(no_core(usedata), aes(se, bias, xmax=scen_max, ymax=scen_max)) +
  contour_plot_base(max_bias = max_bias, max_se = max_se , breaks = breaks) +
  geom_point(aes(color = type), size = 4, shape=19) +
  scale_x_continuous(limits=c(0,scen_max))+
  scale_y_continuous(limits=c(0,scen_max))+
  geom_point(data = gbs, aes(pch=model), col="darkgrey", fill="darkgrey", size=4) +
#  geom_point(data = gbs, size = 7, shape = 1, col="red") +
  scale_shape_manual(breaks = c("ATE", "OLS S", "LASSO INF", "RF INF"),
                     values = c(15, 23, 25, 24)) +
  guides(color = guide_legend(title = "Model Type"),
         shape = guide_legend(title = "Reference"))+
  theme(legend.position = "right",
        legend.justification = "bottom",
        legend.box.just = "left")

p1C


p1D = p1C + ggrepel::geom_text_repel(
  aes(label = modelshort, col = type),
  size = 3, # Increased label size
  max.overlaps = Inf,
  min.segment.length = Inf,
  show.legend = FALSE
)

#ggsave(here::here(paste(sep="_", "graphs/combined/v2meanqueens",scen_dataset, scen_outcome_index, scen_train_set_size, scen_cov_set_size, ".png")), p1D, width = 8, height = 6 , units = "in", bg = 'white')

#ggsave(here::here(paste(sep="_", "graphs/combined/meanqueens",scen_dataset, scen_outcome_index, scen_train_set_size, scen_cov_set_size, ".png")), p, width = 8, height = 6, units = "in", bg = 'white', limitsize=FALSE)


#ggsave(here::here(paste(sep="_", "graphs/combined/cleanmeanqueens",scen_dataset, scen_outcome_index, scen_train_set_size, scen_cov_set_size, ".png")), p, width = 8, height = 6, units = "in", bg = 'white', limitsize=FALSE)


}


```

# Figures 

## Means across queens 

### CA continuous, small covariate set, train set = 1000

```{r run scenario_plot 1}
df_agg$se = df_agg$SE
scenario_plot(scen_dataset="ca", scen_outcome_index = "1", scen_train_set_size = "1000", scen_cov_set_size = "small")
```

### CA continuous, medium covariate set, train set = 1000

```{r  run scenario_plot 2}
scenario_plot(scen_dataset="ca", scen_outcome_index = "1", scen_train_set_size = "1000", scen_cov_set_size = "medium")
```

### CA continuous, large covariate set, train set = 1000

#### NOTE: this removed CDML

```{r  run scenario_plot 3}
scenario_plot(scen_dataset="ca", scen_outcome_index = "1", scen_train_set_size = "1000", scen_cov_set_size = "large")
```

### CA continuous, small covariate set, train set =2000

```{r  run scenario_plot 4}
scenario_plot(scen_dataset="ca", scen_outcome_index = "1", scen_train_set_size = "2000", scen_cov_set_size = "small")
```

### CA continuous, medium covariate set, train set = 2000

```{r  run scenario_plot 5}
scenario_plot(scen_dataset="ca", scen_outcome_index = "1", scen_train_set_size = "2000", scen_cov_set_size = "medium")
```

### CA continuous, large covariate set, train set = 2000

```{r  run scenario_plot 6}
scenario_plot(scen_dataset="ca", scen_outcome_index = "1", scen_train_set_size = "2000", scen_cov_set_size = "large")
```

### ASAP continuous, small covariate set, train set = 1000

```{r  run scenario_plot 7}
scenario_plot(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "1000", scen_cov_set_size = "small")
```


### CA binary, small covariate set, train set = 1000

```{r run scenario_plot 9}
scenario_plot(scen_dataset="ca", scen_outcome_index = "2", scen_train_set_size = 1000, scen_cov_set_size = "small")

```

## Stacked mini plots for CA outcome 1

```{r stack miniplots}
#set scen_max for ca outcome 1
  scen_max = scenario_maximums%>%filter(dataset == "ca"  & outcome_index == "1")%>% select(max) %>% unlist()

  #use scen_max to create euclidean_distance
  euclidean_distance=make_euclidean_distance(scen_max, scen_max)
  
# Adjusting your plot
# Define shapes for each model type

train_size_shape_map = c("1000"=9, "2000"=2, "5000"=10)
cov_set_size_color_map = c("small"="blue", "medium"="orange", "large" = "#696969")
usedata = df_agg %>%
  filter(dataset =="ca" & outcome_index ==1)

p <- ggplot(usedata, aes(SE, bias, xmax=.250, ymax=.250, breaks=.100)) +
  geom_contour(
    data = euclidean_distance,
    aes(x = x, y = y, z = z),
    breaks = c(.050, .100, .150, .200, .250),
    alpha = 0.6
) +
  geom_point(aes(color =cov_set_size, shape=train_set_size),  size = 2)  +
  facet_wrap(~ model) +  # Add facet_wrap 
  theme_minimal() +
  scale_x_continuous(limits=c(0,.350), breaks=c(0,.100, .200))+
  scale_y_continuous(breaks=c(0,.100, .200))+
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    text = element_text(color = "black"),
    plot.title = element_text(size = 12),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12),
    strip.text = element_text(size =8),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)
) +
  labs(
    title = "Mean of Aggregated Bias and SE across Queens\nby Algorithm with RMSE Contouring",
    subtitle = "* ATE queen is excluded",
    col = "Scenario"
) +
  ylab("Bias") +    # Change X-axis title
  xlab("SE")  +     # Change Y-axis title
  scale_color_manual(values=cov_set_size_color_map)+
  scale_shape_manual(values = train_size_shape_map) +
  guides(color = guide_legend(title = "Covariate Set Size"),
         shape = guide_legend(title = "Train Set Size"))

p

# ggsave(here::here(paste0("graphs/combined/stackminiplots.png")), p, width = 8, height = 6, units = "in", bg = 'white', limitsize=FALSE)
```

## ATE and CDML queens only

```{r ATE/CDML queen plots}
# Adjusting your plot
usedata = combined_all %>%
  filter(dataset =="ca") %>%
  filter(outcome_index ==1) %>%
  filter(queen %in% c("ATE", "CDML"))

usedata$queensize = paste0(usedata$queen, ", ", usedata$train_set_size)
combined_shape_map = c("ATE, 1000"=0, "ATE, 2000"=1, "CDML, 1000" = 15, "CDML, 2000"=16)
cov_set_size_color_map = c("small"="blue", "medium"="orange", "large" = "#696969")


  scen_max = scenario_maximums%>%filter(dataset == "ca" & outcome_index == "1")%>% select(max) %>% unlist()
  
  #use scen_max to create euclidean_distance
  euclidean_distance=make_euclidean_distance(scen_max, scen_max)

  p <- ggplot(usedata, aes(se, bias, xmax=.250, ymax=.250, breaks=.100)) +
  geom_contour(
    data = euclidean_distance,
    aes(x = x, y = y, z = z),
    breaks = c(.050, .100, .150, .200, .250),
    alpha = 0.6
) +
  geom_point(aes(color =cov_set_size, shape=queensize),  size = 2)  +
  facet_wrap(~ model) +  # Add facet_wrap 
  theme_minimal() +
  scale_x_continuous(limits=c(0,.350), breaks=c(0,.100, .200))+
  scale_y_continuous(breaks=c(0,.100, .200))+
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    text = element_text(color = "black"),
    plot.title = element_text(size = 12),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text = element_text(size = 12),
    strip.text = element_text(size =8),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)
) +
  labs(
    title = "Aggregated Bias and SE\nby Algorithm with RMSE Contouring",
    subtitle = "ATE and CDML queens only",
    col = "Scenario"
) +
  ylab("Bias") +    # Change X-axis title
  xlab("SE")  +     # Change Y-axis title
  scale_color_manual(values = cov_set_size_color_map) +
  scale_shape_manual(values = combined_shape_map) +
  guides(color = guide_legend(title = "Covariate Set Size"),
         shape = guide_legend(title = "Train Set Size"))

p

# ggsave(here::here(paste0("graphs/combined/ATECDMLonly.png")), p, width = 8, height = 6, units = "in", bg = 'white', limitsize=FALSE)
```

## All queens

```{r create scenario_allqueens}

#create scenario_allqueens function: plot the results from each queen for a given model and scenario 
scenario_allqueens = function(scen_dataset, scen_outcome_index, scen_train_set_size, scen_cov_set_size){ 

  scen_max = scenario_maximums%>%filter(dataset == scen_dataset & outcome_index == scen_outcome_index)%>% select(max) %>% unlist()
  max_bias = scen_max
  max_se = scen_max
  breaks = unlist(scenario_maximums%>%filter(dataset == scen_dataset & outcome_index == scen_outcome_index)%>% select(breaks))

  #use scen_max to create euclidean_distance
  euclidean_distance=make_euclidean_distance(scen_max, scen_max)
  
  usedata = combined_all[(combined_all$dataset ==scen_dataset & combined_all$outcome_index ==scen_outcome_index  & combined_all$train_set_size==scen_train_set_size & combined_all$cov_set_size == scen_cov_set_size),]
  p <- ggplot(usedata, aes(se, bias, xmax=scen_max, ymax=scen_max)) +
    geom_contour(
      data = euclidean_distance,
      aes(x = x, y = y, z = z),
      breaks = breaks,
      alpha = 0.6
) +
    geom_point(aes(color = queen, shape=queen),  size = 2) +
    scale_x_continuous(limits=c(0,scen_max))+
    scale_y_continuous(limits=c(0,scen_max))+ #adding this to remove some outlier CDML
    facet_wrap(~model) +
    theme_minimal() +
    theme(
      plot.background = element_rect(fill = "white", color = NA),
      panel.background = element_rect(fill = "white", color = NA),
      text = element_text(color = "black"),
      plot.title = element_text(size = 16),
      plot.subtitle = element_text(size = 12),
      axis.title = element_text(size = 14),
      legend.title = element_text(size = 14),
      legend.text = element_text(size = 12),
    strip.text = element_text(size =8),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)
) +
    labs(
      title = "Aggregated Bias and SE by Queen\nfor Each Scenario with RMSE Contouring"
) +
    ylab("Bias") +    # Change X-axis title
    xlab("SE")  +     # Change Y-axis title
    scale_shape_manual(values = SHAPE_MAP) +
    guides(color = guide_legend(title = "Queen"),
           shape = guide_legend(title = "Queen"))
  
  print(p)
    
# ggsave(here::here(paste(sep="_","graphs/combined/allqueens",scen_dataset, scen_outcome_index, scen_train_set_size, scen_cov_set_size, ".png")), p, width = 8, height = 6, units = "in", bg = 'white', limitsize=FALSE)
}
```

### CA continuous, small covariate set, train set = 1000

```{r run scenario_allqueens 1}
scenario_allqueens(scen_dataset="ca", scen_outcome_index = "1", scen_train_set_size = "1000", scen_cov_set_size = "small")
```

### CA continuous, medium covariate set, train set = 1000

```{r run scenario_allqueens 2}
scenario_allqueens(scen_dataset="ca", scen_outcome_index = "1", scen_train_set_size = "1000", scen_cov_set_size = "medium")
```

### CA continuous, large covariate set, train set = 1000

```{r run scenario_allqueens 3}
scenario_allqueens(scen_dataset="ca", scen_outcome_index = "1", scen_train_set_size = "1000", scen_cov_set_size = "large")

```

### CA continuous, small covariate set, train set =2000

```{r run scenario_allqueens 4}
scenario_allqueens(scen_dataset="ca", scen_outcome_index = "1", scen_train_set_size = "2000", scen_cov_set_size = "small")

```

### CA continuous, medium covariate set, train set = 2000

```{r run scenario_allqueens 5}

scenario_allqueens(scen_dataset="ca", scen_outcome_index = "1", scen_train_set_size = "2000", scen_cov_set_size = "medium")
```

### CA continuous, large covariate set, train set = 2000

```{r run scenario_allqueens 6}
scenario_allqueens(scen_dataset="ca", scen_outcome_index = "1", scen_train_set_size = "2000", scen_cov_set_size = "large")

```

### ASAP continuous, small covariate set, train set = 1000

#### CDML dropped here because bias = ~50
```{r run scenario_allqueens 7}
scenario_allqueens(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "1000", scen_cov_set_size = "small")

```

### CA binary, small covariate set, train set = 1000

```{r}

scenario_allqueens(scen_dataset="ca", scen_outcome_index = "2", scen_train_set_size = 1000, scen_cov_set_size = "small")

```

### Figures from Luke 

#### Create contour plot

```{r figures from Luke}

# Make contour plot ----
df_agg$se = df_agg$SE
df_set_1 <- filter(df_agg, set_id == "ca-1-large-1000")
df_set_2 <- filter(df_agg, set_id == "ca-1-large-2000")

#max_bias = max(df_set_1$bias, df_set_2$bias)
#max_se = max(df_set_1$se, df_set_2$se)
  scen_max = scenario_maximums%>%filter(dataset == "ca" & outcome_index == "1")%>% select(max) %>% unlist()
  max_bias = scen_max
  max_se = scen_max
  breaks = unlist(scenario_maximums%>%filter(dataset == "ca" & outcome_index == "1")%>% select(breaks))


p1 <- make_contour_plot(df_set_1, max_bias=max_bias, max_se=max_se , breaks = breaks)
p1

p2 <- make_contour_plot(df_set_2, max_bias=max_bias, max_se = max_se, breaks = breaks)
p2



# Alternate labeling approaches? ----

p1B <- make_contour_plot(df_set_1, max_bias=max_bias, max_se=max_se, breaks = breaks, add_labels = FALSE)
p1B + ggrepel::geom_text_repel(
  aes(label = modelshort, col = type),
  size = 2, # Increased label size
  max.overlaps = Inf,
  show.legend = FALSE
)


gbs = filter(df_set_1, model %in% c("ATE", "OLS S", "LASSO INF", "RF INF"))
gbs$model

```

#### p1C (TODO: better title?) 

```{r p1C}

p1C <- ggplot(no_core(df_set_1), aes(se, bias, xmax=max_se, ymax=max_bias)) +
  contour_plot_base(max_bias = max_bias, max_se = max_se , breaks = breaks) +
  geom_point(aes(color = type), size = 4, shape=19) +
  geom_point(data = gbs, aes(pch=model), col="darkgrey", fill="darkgrey", size=4) +
#  geom_point(data = gbs, size = 7, shape = 1, col="red") +
  scale_shape_manual(breaks = c("ATE", "OLS S", "LASSO INF", "RF INF"),
                     values = c(15, 23, 25, 24)) +
  guides(color = guide_legend(title = "Model Type"),
         shape = guide_legend(title = "Reference"))
p1C


p1C + ggrepel::geom_text_repel(
  aes(label = modelshort, col = type),
  size = 3, # Increased label size
  max.overlaps = Inf,
  min.segment.length = Inf,
  show.legend = FALSE
)

#ggsave(here::here("graphs/possible_clean_plot_1.pdf"))


```

#### Animation (isn't working for now)

```{r animation}
if (FALSE) {
  # This isn't working
  
# Trying out animation ----

library(ggplot2)
library(gganimate)

df_range = bind_rows(set1 = df_set_1, set2 = df_set_2, .id = "set") %>%
 # dplyr::select(-n, -rmse) %>%
  group_by(model, type, modelshort)

# Plot and animate

p <- ggplot(df_range, aes(se, bias, xmax=max_se, ymax=max_bias)) +
  geom_point(aes(color = type, shape=type),  size = 4)  +
  transition_states(set, transition_length = 2, state_length = 1, wrap=FALSE) +
  ease_aes('linear') +
  labs(title = "Scenario: {closest_state}") +
  contour_plot_base(max_bias = max_bias, max_se = max_se , breaks = breaks) +
  theme(legend.position = "none")

p


anim <- animate(p, duration = 5, fps = 10, width = 600, height = 400)

gganimate::anim_save(here::here("graphs/initial_animation.gif"))



  # Extract the first frame
  first_frame <- anim::anim_save(anim, start_pause = 1, nframes = 1)
  
  # Extract the last frame
  last_frame <- anim_save(anim, end_pause = 1, nframes = 1)
  
  # Add labels to the first frame
  first_frame_labeled <- ggplot_build(first_frame) +
    ggrepel::geom_label_repel(
      aes(label = after_stat(ifelse(set %in% c("set1", "set2"), modelshort, NA)), color = type),
      size = 3, # Increased label size
      box.padding = 0.75,
      point.padding = 0.25,
      max.overlaps = Inf,
      show.legend = FALSE
)   
  
  geom_label_repel(aes(label = modelshort, color = type), size = 5)
  
  # Add labels to the last frame
  last_frame_labeled <- ggplot_build(last_frame) +
    geom_label_repel(aes(label = modelshort, color = type), size = 5)
  
  # You can now save or display these labeled frames
#  ggsave("first_frame_with_labels.png", plot = first_frame_labeled)
#  ggsave("last_frame_with_labels.png", plot = last_frame_labeled)
}

```

#### "Trails from last plot" plot (two versions) ----

```{r trails from last plot}
d_b = df_set_2 %>%
  ungroup() %>%
  dplyr::select(-c(set_id:train_set_size)) %>%
  left_join(dplyr::select(ungroup(df_set_1), model, bias, se), 
             by = "model",
             suffix = c("", "old"))


plt <-  ggplot(d_b, aes(se, bias, xmax=max_se, ymax=max_bias)) +
  geom_segment(aes(x = seold, y = biasold, xend = se, yend = bias),
               arrow = arrow(length = unit(0.2, "cm")), lwd = 1, col="darkgrey") +
  geom_point(aes(color = type, shape=type, size = as.numeric(3+1*baseline)), fill="grey") + 
  contour_plot_base(max_bias = max_bias, max_se = max_se , breaks = breaks) +
  labs(title = "Trails of Models from 1000 to 2000") + 
  scale_size_identity() +
  guides(size="none")
plt


# A second version

pltB <-  ggplot(d_b, aes(se, bias, xmax=max_se, ymax=max_bias)) +
  #geom_point(aes(color = type, shape=type, size = as.numeric(4+2*baseline)), fill="grey") + 
  geom_segment(aes(x = seold, y = biasold, xend = se, yend = bias),
               arrow = arrow(length = unit(0.2, "cm")), lwd = 1, col="lightgrey") +
  geom_point(data = no_core(d_b), aes(color = type), size = 4, shape=19) +
  geom_point(data = only_core(d_b), aes(pch=model), col="darkgrey", fill="darkgrey", size=4) +
  contour_plot_base(max_bias = max_bias, max_se = max_se , breaks = breaks) +
  labs(title = "Trails of Models from 1000 to 2000") + 
  scale_size_identity() +
  scale_shape_manual(breaks = c("ATE", "OLS S", "LASSO INF", "RF INF"),
                     values = c(15, 23, 25, 24)) +
  guides(color = guide_legend(title = "Model Type"),
         shape = guide_legend(title = "Reference"),
         size="none")
pltB


pltB + ggrepel::geom_text_repel(
  aes(label = modelshort, col = type),
  size = 3, # Increased label size
  max.overlaps = Inf,
  min.segment.length = Inf,
  show.legend = FALSE
)

pltB

#ggsave(here::here("graphs/possible_clean_plot_2.pdf"))