---
title: "Combined Results Template - Work in Progress"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    fig_caption: yes
    fig_height: 8
    fig_width: 10
    highlight: pygments
    theme: spacelab
    toc: yes
    toc_depth: 6
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '6'
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}

library(writexl)
knitr::opts_chunk$set( echo = TRUE )
```

# Set up

```{r source previous script,  include=FALSE}
# Load script 08
source(here::here("simulation_pipeline/08_run_simulation.R"))
```

```{r run read_and_aggregate}
#NC 12-2-24: this code is now in  a separate combining script, just loading the file now
combined_all = read.xlsx(here::here("graphs/combined/combined_all.xlsx"))
#combined_all = read.xlsx(here::here("graphs/combined/combined_all_asap_cont.xlsx"))

```

```{r specify axis maximums by simulation run and create euclidean_distance}

  #specifying axis maximums (x and y both) and breaks by datasets
  #update this when adding new datasets/outcomes
  scenario_maximums = rbind(
    data.frame(dataset = "asap", outcome_index = "2", max = 1.2, max_bias = 1.2, max_se = 1.2, breaks = I(list(c(0,.2,.4,.6,.8, 1))),max_agg = .35, max_bias_agg = .35, max_se_agg = .35, breaks_agg = I(list(c(0,.1,.2,.3)))),
    data.frame(dataset = "asap", outcome_index = "1", max = 1, max_bias = 1, max_se = 1, breaks = I(list(c(0,.2,.4,.6,.8))),max_agg = 1, max_bias_agg = 1, max_se_agg = 1, breaks_agg = I(list(c(0,.2,.4,.6,.8)))))

```

```{r}

df = combined_all
df$set_id = paste( df$dataset, df$outcome_index, df$cov_set_size, df$train_set_size, sep="-" )

ALL_MODELS <- unique( df$model )

# Function to make RMSE contour plots ----

TYPE_SHAPE_MAP <- c(
  "ATE" = 20, "OLS S" = 18, 
  "INF" = 2, "RF" = 3, "CDML" = 8,
  "LASSO" = 10, "SL" = 16,
  "XGBOOST" = 1, "BART" = 0
)

TYPE_COLOR_MAP <- c(
  "ATE" = "black", "OLS S" = "black", 
  "INF" = "darkgrey", "RF" = "#E69F00", "CDML" = "#F0E442",
  "LASSO" = "#009E73", "SL" = "#D55E00",
  "XGBOOST" = "#CC79A7", "BART" = "#0072B2" # "#56B4E9"
)
LEGEND_COLORS = setdiff( names(TYPE_COLOR_MAP), c("LASSO INF", "RF INF", "ATE", "OLS S") )

# For individual methods
SHAPE_MAP <- c(
  "ATE" = 0, "OLS S" = 1, 
  "RF INF" = 2, "RF T" = 3, "RF MOM IPW" = 4, "RF MOM DR" = 5, 
  "CF" = 6, "CF LC" = 7, "CDML" = 8, "LASSO INF" = 9, "LASSO T" = 10, "LASSO MOM IPW" = 11, 
  "LASSO MOM DR" = 12, "LASSO MCM" = 13, "LASSO MCM EA" = 14, "LASSO R" = 15, 
  "SL T" = 16, "SL S" = 17, "XGBOOST S" = 18, "XGBOOST R" = 19, "BART T" = 20, "BART S" = 21
)

old_type_shape_map <- c(
  "ATE" = 18, "OLS S" = 20, "INF" = 2, "RF" = 3, "CDML" = 8,  "LASSO" = 10, "SL" = 16, "XGBOOST" = 0, "BART" = 1
)
old_shape_map <- c(
  "ATE" = 0, "OLS S" = 1, "RF INF" = 2, "RF T" = 3, "RF MOM IPW" = 4, "RF MOM DR" = 5, 
  "CF" = 6, "CF LC" = 7, "CDML" = 8, "LASSO INF" = 9, "LASSO T" = 10, "LASSO MOM IPW" = 11, 
  "LASSO MOM DR" = 12, "LASSO MCM" = 13, "LASSO MCM EA" = 14, "LASSO R" = 15, 
  "SL T" = 16, "SL S" = 17, "XGBOOST S" = 18, "XGBOOST R" = 19, "BART T" = 20, "BART S" = 21
)


```





```{r create scenario_plot, include=FALSE}


all_scenarios = df

# Mean of all queens that are already aggregated excluding ATE
all_scenarios_agg = df %>%
                filter(!(queen %in% c("ATE", "LASSO MCM EA")), ,
                       !(model %in% c("SL S", "SL T", "XGBOOST S", "XGBOOST R"))) %>% 
                group_by(set_id, dataset, outcome_index, cov_set_size, train_set_size,
            model, type, modelshort) %>%
                summarise(bias = mean(bias),
                          SE = mean(se),
                          RMSE = mean(rmse),
                          .groups = "drop")


all_scenarios_agg$se = all_scenarios_agg$SE
# Update naming and tags for clarity and shorter names ----
# Keep ATE and OLS as baseline, and drop labels for the baseline models
all_scenarios_agg <- mutate( all_scenarios_agg,
                  baseline = model %in% c( "ATE", "OLS S", "LASSO INF", "RF INF" ),
                  modelshort = ifelse( baseline, "", modelshort ) )
all_scenarios_agg$modelshort <- str_replace( all_scenarios_agg$modelshort, "MOM ", "" )
all_scenarios_agg$modelshort <- str_replace( all_scenarios_agg$modelshort, "CF LC", "CF-LC" )
all_scenarios_agg$modelshort <- str_replace( all_scenarios_agg$modelshort, "MCM EA", "EA" )

table( all_scenarios_agg$modelshort )

```

# Figures 

## Means across queens 

### ASAP continuous, small covariate set, train set = 1000

```{r run scenario_plot 1}



scenario_plot(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "1000", scen_cov_set_size = "small")

#all_scenarios_agg_save = all_scenarios_agg
# all_scenarios_agg = all_scenarios_agg_[all_scenarios_agg_use$model=="ATE",]




```

### ASAP continuous, medium covariate set, train set = 1000

```{r  run scenario_plot 2}
scenario_plot(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "1000", scen_cov_set_size = "medium")
```

### ASAP continuous, large covariate set, train set = 1000

#### NOTE: this removed CDML

```{r  run scenario_plot 3}
scenario_plot(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "1000", scen_cov_set_size = "large")
```

### ASAP continuous, small covariate set, train set =2000

```{r  run scenario_plot 4}
scenario_plot(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "2000", scen_cov_set_size = "small")

```

### ASAP continuous, medium covariate set, train set = 2000

```{r  run scenario_plot 5}
scenario_plot(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "2000", scen_cov_set_size = "medium")
```

### ASAP continuous, large covariate set, train set = 2000

```{r  run scenario_plot 6}
scenario_plot(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "2000", scen_cov_set_size = "large")
```



## Stacked mini plots for ASAP outcome 2

```{r stack miniplots}

stack_miniplots(scen_dataset= "asap", scen_outcome_index = "2", scen_train_set_size = "2000", scen_cov_set_size = "small")
```
## ATE and CDML queens only

```{r ATE/CDML queen plots}
plot_two_queens(scen_dataset= "asap", scen_outcome_index = "2", queen1="ATE", queen2="CDML")

```

## All queens

### ASAP continuous, small covariate set, train set = 1000

```{r run scenario_allqueens 1}
scenario_allqueens(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "1000", scen_cov_set_size = "small")
```

### ASAP continuous, medium covariate set, train set = 1000

```{r run scenario_allqueens 2}
scenario_allqueens(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "1000", scen_cov_set_size = "medium")
```

### ASAP continuous, large covariate set, train set = 1000

```{r run scenario_allqueens 3}
scenario_allqueens(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "1000", scen_cov_set_size = "large")

```

### ASAP continuous, small covariate set, train set =2000

```{r run scenario_allqueens 4}
scenario_allqueens(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "2000", scen_cov_set_size = "small")

```

### ASAP continuous, medium covariate set, train set = 2000

```{r run scenario_allqueens 5}

scenario_allqueens(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "2000", scen_cov_set_size = "medium")
```

### ASAP continuous, large covariate set, train set = 2000

```{r run scenario_allqueens 6}
scenario_allqueens(scen_dataset="asap", scen_outcome_index = "2", scen_train_set_size = "2000", scen_cov_set_size = "large")

```

### ASAP binary, small covariate set, train set = 1000 (leaving out for now)

```{r run scenario_allqueens 7}
#scenario_allqueens(scen_dataset="asap", scen_outcome_index = "1", scen_train_set_size = "1000", scen_cov_set_size = "small")

```


### Figures from Luke 

```{r figures from Luke}

# Make contour plot ----
#all_scenarios_agg$se = all_scenarios_agg$SE
df_set_1 <- filter( all_scenarios_agg, set_id == "asap-2-large-1000" )
df_set_2 <- filter( all_scenarios_agg, set_id == "asap-2-large-5000" )

#max_bias = max( df_set_1$bias, df_set_2$bias )
#max_se = max( df_set_1$se, df_set_2$se )
  scen_max = scenario_maximums%>%filter(dataset == "asap" & outcome_index == "2")%>% select(max) %>% unlist()
  max_bias = scen_max
  max_se = scen_max
  breaks = unlist(scenario_maximums%>%filter(dataset == "asap" & outcome_index == "2")%>% select(breaks))


p1 <- make_contour_plot( df_set_1, max_bias=max_bias, max_se=max_se , breaks = breaks)
p1

p2 <- make_contour_plot( df_set_2, max_bias=max_bias, max_se = max_se, breaks = breaks )
p2



# Alternate labeling approaches? ----

p1B <- make_contour_plot( df_set_1, max_bias=max_bias, max_se=max_se, breaks = breaks, add_labels = FALSE )
p1B + ggrepel::geom_text_repel(
  aes(label = modelshort, col = type),
  size = 2, # Increased label size
  max.overlaps = Inf,
  show.legend = FALSE
)


gbs = filter( df_set_1, model %in% c( "ATE", "OLS S", "LASSO INF", "RF INF" ) )
gbs$model

p1C <- ggplot( no_core( df_set_1 ), aes(se, bias, xmax=max_se, ymax=max_bias) ) +
  contour_plot_base( max_bias = max_bias, max_se = max_se , breaks = breaks) +
  geom_point(aes(color = type), size = 4, shape=19 ) +
  geom_point( data = gbs, aes(pch=model), col="darkgrey", fill="darkgrey", size=4 ) +
#  geom_point( data = gbs, size = 7, shape = 1, col="red" ) +
  scale_shape_manual(breaks = c( "ATE", "OLS S", "LASSO INF", "RF INF" ),
                     values = c( 15, 23, 25, 24 ) ) +
  guides(color = guide_legend(title = "Model Type"),
         shape = guide_legend(title = "Reference") )
p1C


p1C + ggrepel::geom_text_repel(
  aes(label = modelshort, col = type),
  size = 3, # Increased label size
  max.overlaps = Inf,
  min.segment.length = Inf,
  show.legend = FALSE
)

#ggsave( here::here( "graphs/possible_clean_plot_1.pdf" ) )




if ( FALSE ) {
  # This isn't working
  
# Trying out animation ----

library(ggplot2)
library(gganimate)

df_range = bind_rows( set1 = df_set_1, set2 = df_set_2, .id = "set" ) %>%
 # dplyr::select( -n, -rmse ) %>%
  group_by( model, type, modelshort )

# Plot and animate

p <- ggplot( df_range, aes(se, bias, xmax=max_se, ymax=max_bias) ) +
  geom_point(aes(color = type, shape=type),  size = 4)  +
  transition_states( set, transition_length = 2, state_length = 1, wrap=FALSE) +
  ease_aes('linear') +
  labs(title = "Scenario: {closest_state}") +
  contour_plot_base( max_bias = max_bias, max_se = max_se , breaks = breaks ) +
  theme( legend.position = "none" )

p


anim <- animate(p, duration = 5, fps = 10, width = 600, height = 400)

gganimate::anim_save( here::here( "graphs/initial_animation.gif") )



  # Extract the first frame
  first_frame <- anim::anim_save(anim, start_pause = 1, nframes = 1)
  
  # Extract the last frame
  last_frame <- anim_save(anim, end_pause = 1, nframes = 1)
  
  # Add labels to the first frame
  first_frame_labeled <- ggplot_build(first_frame) +
    ggrepel::geom_label_repel(
      aes( label = after_stat(ifelse(set %in% c("set1", "set2"), modelshort, NA)), color = type),
      size = 3, # Increased label size
      box.padding = 0.75,
      point.padding = 0.25,
      max.overlaps = Inf,
      show.legend = FALSE
    )   
  
  geom_label_repel(aes(label = modelshort, color = type), size = 5)
  
  # Add labels to the last frame
  last_frame_labeled <- ggplot_build(last_frame) +
    geom_label_repel(aes(label = modelshort, color = type), size = 5)
  
  # You can now save or display these labeled frames
#  ggsave("first_frame_with_labels.png", plot = first_frame_labeled)
#  ggsave("last_frame_with_labels.png", plot = last_frame_labeled)
  
  
  
  
}


# "Trails from last plot" plot ----

d_b = df_set_2 %>%
  ungroup() %>%
  dplyr::select( -c( set_id:train_set_size ) ) %>%
  left_join( dplyr::select( ungroup( df_set_1 ), model, bias, se ), 
             by = "model",
             suffix = c( "", "old" ) )


plt <-  ggplot( d_b, aes(se, bias, xmax=max_se, ymax=max_bias) ) +
  geom_segment(aes(x = seold, y = biasold, xend = se, yend = bias),
               arrow = arrow(length = unit(0.2, "cm")), lwd = 1, col="darkgrey") +
  geom_point(aes(color = type, shape=type, size = as.numeric(3+1*baseline) ), fill="grey" ) + 
  contour_plot_base( max_bias = max_bias, max_se = max_se , breaks = breaks) +
  labs( title = "Trails of Models from 1000 to 2000" ) + 
  scale_size_identity() +
  guides( size="none" )
plt


# A second version

pltB <-  ggplot( d_b, aes(se, bias, xmax=max_se, ymax=max_bias) ) +
  #geom_point(aes(color = type, shape=type, size = as.numeric(4+2*baseline) ), fill="grey" ) + 
  geom_segment(aes(x = seold, y = biasold, xend = se, yend = bias),
               arrow = arrow(length = unit(0.2, "cm")), lwd = 1, col="lightgrey") +
  geom_point( data = no_core( d_b ), aes(color = type), size = 4, shape=19 ) +
  geom_point( data = only_core( d_b ), aes(pch=model), col="darkgrey", fill="darkgrey", size=4 ) +
  contour_plot_base( max_bias = max_bias, max_se = max_se , breaks = breaks ) +
  labs( title = "Trails of Models from 1000 to 2000" ) + 
  scale_size_identity() +
  scale_shape_manual(breaks = c( "ATE", "OLS S", "LASSO INF", "RF INF" ),
                     values = c( 15, 23, 25, 24 ) ) +
  guides(color = guide_legend(title = "Model Type"),
         shape = guide_legend(title = "Reference"),
         size="none" )
pltB


pltB + ggrepel::geom_text_repel(
  aes(label = modelshort, col = type),
  size = 3, # Increased label size
  max.overlaps = Inf,
  min.segment.length = Inf,
  show.legend = FALSE
)

pltB

#ggsave( here::here( "graphs/possible_clean_plot_2.pdf"))