---
title: "Template Based on SREE Plots - Work in Progress"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    fig_caption: yes
    fig_height: 8
    fig_width: 10
    highlight: pygments
    theme: spacelab
    toc: yes
    toc_depth: 6
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '6'
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}

library(writexl)
knitr::opts_chunk$set( echo = TRUE )
```

# Set up

```{r source previous script,  include=FALSE}
# Load script 08
source(here::here("simulation_pipeline/08_run_simulation.R"))


#read in file 
combined_all = read.xlsx(here::here("graphs/combined/combined_all_asap_cont.xlsx"))



# SREE 2024 Plots and Results
#
# This script makes all the plots in the SREE 2024 presentation,
# including the regression coefficient plots and the contour plots

library( tidyverse )
library(ggplot2)

library(cowplot) # For making legend-only subplot

source( here::here( "graphs/load_simulation_results.R" ) )
source( here::here( "graphs/contour_plot_code.R" ) )



# Check if the "sree2024" directory exists, if not, create it
if (!dir.exists(here::here("graphs/sree2024"))) {
  dir.create(here::here("graphs/sree2024"))
}



asap2_agg = filter(df_agg, 
                 outcome_index == 2,
                 dataset == "asap" )
table( df$set_id )

max_bias = max( df$bias )
max_se = max( df$se )

# hard coded to make all plots on same dimensions
max_bias = .5
max_se = .5


# Plot of just the RF T queen ----
table( df$queen )

dd = filter( df, cov_set_size == "small", train_set_size == 1000, queen == "RF T" )

p1C <- ggplot( no_core( dd ), aes(se, bias) ) +
  contour_plot_base( max_bias = max_bias, max_se = max_se, step = .1, include_scales = FALSE ) +
  geom_point( aes(color = type), size = 4, shape=19 ) +
  geom_point( data = only_core( dd ), aes(pch=model), col="darkgrey", fill="darkgrey", size=4 ) +
  #  geom_point( data = gbs, size = 7, shape = 1, col="red" ) +
  scale_shape_manual(breaks = c( "ATE", "OLS S", "LASSO INF", "RF INF" ),
                     values = c( 15, 23, 25, 24 ) ) +
  guides(color = guide_legend(title = "Model Type"),
         shape = guide_legend(title = "Reference") ) +
  coord_fixed( xlim=c(0, max_se) ) 

```

# contour_RFT_1000_legend.pdf

```{r contour_RFT_1000_legend.pdf}
p1C + ggrepel::geom_text_repel(
  aes(label = modelshort, col = type),
  size = 3, # Increased label size
  max.overlaps = Inf,
  min.segment.length = Inf,
  show.legend = FALSE
)



# Extract the legend and save it ----

# This makes it easy to arrange things on slides by giving a separate
# image for the legend.
legend <- cowplot::get_legend(p1C)

# Plot only the legend
legend_plot <- ggdraw(legend)
# legend_plot

# Save the legend as a separate image
#ggsave("graphs/sree2024/legend_only.png", plot = legend_plot, width = 5, height = 5)



# Now make the plot without the legend

dd = filter( df, cov_set_size == "small", train_set_size == 1000, queen == "RF T" )
p1C <- ggplot( no_core( dd ), aes(se, bias) ) +
  contour_plot_base( max_bias = max_bias, max_se = max_se, step = .1, include_scales = FALSE ) +
  geom_point( aes(color = type), size = 4, shape=19 ) +
  geom_point( data = only_core( dd ), aes(pch=model), col="darkgrey", fill="darkgrey", size=4 ) +
  #  geom_point( data = gbs, size = 7, shape = 1, col="red" ) +
  scale_shape_manual(breaks = c( "ATE", "OLS S", "LASSO INF", "RF INF" ),
                     values = c( 15, 23, 25, 24 ) ) +
  guides(color = guide_legend(title = "Model Type"),
         shape = guide_legend(title = "Reference") ) +
  coord_fixed( xlim=c(0, max_se) ) +
  theme( legend.position = "none" )

```

# contour_RFT_1000.pdf

```{r contour_RFT_1000.pdf}
p1C + ggrepel::geom_text_repel(
  aes(label = modelshort, col = type),
  size = 3, # Increased label size
  max.overlaps = Inf,
  min.segment.length = Inf,
  show.legend = FALSE
)
#ggsave( filename = "graphs/sree2024/contour_RFT_1000.pdf", width = IMAGE_WIDTH, height = 5 )



# Plot averaged across queens ----

table( df$queen )

dd = filter( asap2_agg, outcome_index == 2, 
             cov_set_size == "small", 
             train_set_size == 1000 )

p1C <- ggplot( no_core( dd ), aes(se, bias) ) +
  contour_plot_base( max_bias = max_bias, max_se = max_se, step = .1, include_scales = FALSE ) +
  geom_point( aes(color = type), size = 4, shape=19 ) +
  geom_point( data = only_core( dd ), aes(pch=model), col="darkgrey", fill="darkgrey", size=4 ) +
  #  geom_point( data = gbs, size = 7, shape = 1, col="red" ) +
  scale_shape_manual(breaks = c( "ATE", "OLS S", "LASSO INF", "RF INF" ),
                     values = c( 15, 23, 25, 24 ) ) +
  guides(color = guide_legend(title = "Model Type"),
         shape = guide_legend(title = "Reference") ) +
  coord_fixed( xlim=c(0, max_se) ) +
  theme( legend.position = "none" )

```

# contour_all_1000.pdf

```{r contour_all_1000.pdf}

p1C + ggrepel::geom_text_repel(
  aes(label = modelshort, col = type),
  size = 3, # Increased label size
  max.overlaps = Inf,
  min.segment.length = Inf,
  show.legend = FALSE
)

#ggsave( filename = "graphs/sree2024/contour_all_1000.pdf", width = IMAGE_WIDTH, height = 5 )



# Moving to large covariate set plot  ----

d_b = make_trail_set( filter( asap2_agg, 
                              train_set_size == 1000,
                              outcome_index == 2,
                              cov_set_size=="small"),
                      filter( asap2_agg, 
                              train_set_size == 1000,
                              outcome_index == 2,
                              cov_set_size=="large" ) )


pltB <-  ggplot( no_core( d_b ), aes(se, bias) ) +
  contour_plot_base( max_bias = max_bias, max_se = max_se, step = .1,include_scales = FALSE ) +
  geom_segment( data= d_b, aes(x = se_pre, y = bias_pre, xend = se, yend = bias),
                #arrow = arrow(length = unit(0.2, "cm")),
                lwd = 1, col="lightgrey") +
  geom_point( data = no_core( d_b ), aes(color = type), size = 4, shape=19 ) +
  geom_point( data = only_core( d_b ), aes(pch=model), col="darkgrey", fill="darkgrey", size=4 ) +
  #labs( title = "Trails of Models from 1000 to 5000 training size",
  #      subtitle = "Aggregated over scenarios and queens" ) + 
  #scale_size_identity() +
  scale_shape_manual(breaks = c( "ATE", "OLS S", "LASSO INF", "RF INF" ),
                     values = c( 15, 23, 25, 24 ) ) +
  guides(color = guide_legend(title = "Model Type"),
         shape = guide_legend(title = "Reference") ) +
  coord_fixed( xlim=c(0, max_se) ) +
  theme( legend.position = "none" )

pltB


``` 

# contour_trail_to_large.pdf

```{r contour_trail_to_large.pdf}
pltB + ggrepel::geom_text_repel(
  aes(label = modelshort, col = type),
  size = 3, # Increased label size
  max.overlaps = Inf,
  min.segment.length = Inf,
  show.legend = FALSE
)

#ggsave( filename = "graphs/sree2024/contour_trail_to_large.pdf", 
 #       width = IMAGE_WIDTH, height = 5 )







# Moving to large training set plot  ----

d_b = make_trail_set( filter( asap2_agg, 
                              outcome_index == 2,
                              train_set_size == 1000,
                              cov_set_size=="large"),
                      filter( asap2_agg, train_set_size == 5000, cov_set_size=="large" ) )


pltB <-  ggplot( no_core( d_b ), aes(se, bias) ) +
  contour_plot_base( max_bias = max_bias, max_se = max_se,step = .1, include_scales = FALSE ) +
  geom_segment( data= d_b, aes(x = se_pre, y = bias_pre, xend = se, yend = bias),
                #arrow = arrow(length = unit(0.2, "cm")),
                lwd = 1, col="lightgrey") +
  geom_point( data = no_core( d_b ), aes(color = type), size = 4, shape=19 ) +
  geom_point( data = only_core( d_b ), aes(pch=model), col="darkgrey", fill="darkgrey", size=4 ) +
  #labs( title = "Trails of Models from 1000 to 5000 training size",
  #      subtitle = "Aggregated over scenarios and queens" ) + 
  #scale_size_identity() +
  scale_shape_manual(breaks = c( "ATE", "OLS S", "LASSO INF", "RF INF" ),
                     values = c( 15, 23, 25, 24 ) ) +
  guides(color = guide_legend(title = "Model Type"),
         shape = guide_legend(title = "Reference") ) +
  coord_fixed( xlim=c(0, max_se) ) +
  theme( legend.position = "none" )

pltB


```

# contour_trail_to_5000.pdf

```{r contour_trail_to_5000.pdf}
pltB + ggrepel::geom_text_repel(
  aes(label = modelshort, col = type),
  size = 3, # Increased label size
  max.overlaps = Inf,
  min.segment.length = Inf,
  show.legend = FALSE
)

#ggsave( filename = "graphs/sree2024/contour_trail_to_5000.pdf", width = IMAGE_WIDTH, height = 5 )




# Binary outcome ----

bin <- df %>% 
  dplyr::filter( outcome_index == 2 )
table( bin$model )

filter( df, outcome_index == 2, model == "LASSO INF" ) %>%
  dplyr::select( -bias, -rmse, -se, -outcome_index )

filter( df, outcome_index == 2, model == "BART T" ) %>%
  dplyr::select( -bias, -rmse, -se, -outcome_index )
# 
# if ( FALSE ) {
#   
#   asap <- df %>% 
#     dplyr::filter( dataset == "asap" )
#   table( asap$model )
#   
#   group_by( model, modelshort, type, baseline ) %>%
#     summarise( n = n(),
#                bias = sqrt( mean(bias^2 ) ),
#                se = sqrt( mean( se^2 ) ),
#                rmse = sqrt( mean( rmse^2 ) ), .groups = "drop" )
#   
#   bin <- df_agg %>% 
#     dplyr::filter( outcome_index == 2, dataset == "ca" )
#   
#   dd = bin
#   max_bias = 0.15 #max( dd$bias )
#   max_se = 0.15 #max( dd$se )
#   p1C <- ggplot( no_core( dd ), aes(se, bias) ) +
#     contour_plot_base( max_bias = max_bias, max_se = max_se, include_scales = FALSE, step = 0.025 ) +
#     geom_point( aes(color = type), size = 4, shape=19 ) +
#     geom_point( data = only_core( dd ), aes(pch=model), col="darkgrey", fill="darkgrey", size=4 ) +
#     #  geom_point( data = gbs, size = 7, shape = 1, col="red" ) +
#     scale_shape_manual(breaks = c( "ATE", "OLS S", "LASSO INF", "RF INF" ),
#                        values = c( 15, 23, 25, 24 ) ) +
#     guides(color = guide_legend(title = "Model Type"),
#            shape = guide_legend(title = "Reference") ) +
#     coord_fixed( xlim=c(0, max_se) ) +
#     theme( legend.position = "none" )
#   
#   p1C + ggrepel::geom_text_repel(
#     aes(label = modelshort, col = type),
#     size = 3, # Increased label size
#     max.overlaps = Inf,
#     min.segment.length = Inf,
#     show.legend = FALSE
#   )
#   ggsave( filename = "graphs/sree2024/binary_ca.pdf", width = IMAGE_WIDTH, height = 5 )
#   
# }


# By queen ----


df <- mutate( df, is_ATE = ifelse( queen == "ATE", "ATE", "Not ATE" ) )

table( df$model )

```


# all_queen_plot.pdf 

```{r all_queen_plot.pdf}
ggplot( df, aes(se, bias, xmax=max_se, ymax=max_bias,  col=is_ATE, pch= ) ) +
  facet_wrap( ~ model, nrow=3 ) +
  contour_plot_base( max_bias = max_bias, max_se = max_bias,step= .1, include_scales = FALSE) +
  geom_point( size = 1, shape=19, alpha=0.8 ) +
  labs( #title = "All queens for all models across all CA sets",
    color = "ATE Queen" ) + 
  scale_size_identity() +
  scale_color_manual(breaks = c("ATE", "Not ATE"),
                     values = c( "red", "black" ) ) +
  theme(panel.grid.minor = element_blank(),
        legend.position = "none" )


#ggsave( filename = "graphs/sree2024/all_queen_plot.pdf", width = 11, height = 6 )





# Performance across 6 scenarios

table( asap2_agg$model )


# ggplot( asap2_agg, aes( cov_set_size, rmse, group=as.factor(train_set_size), col=as.factor(train_set_size) ) ) +
#   facet_wrap( ~model ) +
#   geom_line() + geom_point() +
#   theme_minimal() +
#   theme( panel.grid.minor = element_blank() )




# Regression plots ----

# These plots plot the results of regressing rmse, se, and bias onto
# the simulation conditions and queen and model.
#
# We fit three models, and then make plots of the different families
# of coefficients.


# Prep data for regression by making ATE the reference category for
# both queen and model.
df
df_sub <- df %>%
  dplyr::filter( outcome_index == 2,
                 dataset == "asap" ) %>%
  mutate( model = relevel( factor( model ), ref = "ATE" ),
          queen = relevel( factor( queen ), ref = "ATE" ),
          cov_set_size = factor( cov_set_size, levels = c("small","medium","large" ) ),
          N5000 = 0 + (train_set_size==5000),
  ) %>%
  dplyr::filter( !str_detect( model, "INF"))


## Match queen and model for "home field advantage" flag ----


# table( df_sub$model )
# table( df_sub$queen )
# 
# setdiff( unique( df_sub$model ), 
#          unique( df_sub$queen ) )

# This tries to get which models are "at home" with which queens.
#
# TODO: Update this to generate a "linear model/linear queen" match.
home <- function( model, queen ) {
  if ( model == queen ) {
    return( TRUE )
  }
  if ( model == "BART S" ) {
    return (queen == "BART T" )
  }
  if ( str_detect( model, "LASSO" ) ) {
    return( str_detect( queen, "LASSO" ) )
  }
  if ( model == "SL S" ) {
    return (queen == "SL T" )
  }
  if ( str_detect( model, "RF MOM" ) ) {
    return( queen == "RF MOM IPW" )
  }
  if ( model == "CF LC" ) {
    return( queen == "CF" )
  }
  return( FALSE )
}

# testing code
home( df_sub$model[[4]], df_sub$queen[[4]] )

# Calculate home for each model
df_sub <- mutate( df_sub,
                  home = map2_dbl( model, queen, home ) )


## Fit the linear models & make result tables ----

M_rmse = lm( rmse ~ 1 + model + queen + cov_set_size + N5000 + home, data = df_sub )
M_se = lm( se ~ 1 + model + queen + cov_set_size + N5000 + home, data = df_sub )
M_bias = lm( bias ~ 1 + model + queen + cov_set_size + N5000 + home, data = df_sub )



library( broom )
c_rmse <- tidy( M_rmse ) %>%
  dplyr::select( term, estimate, std.error )
c_se <- tidy( M_se ) %>%
  dplyr::select( term, estimate, std.error )
c_bias <- tidy( M_bias ) %>%
  dplyr::select( term, estimate, std.error )

cs <- bind_rows( rmse = c_rmse, se = c_se, bias = c_bias, .id = "measure" )
cs$term = str_replace( cs$term, "cov_set_size", "cov_" )
cs$term = str_replace( cs$term, "queen", "Q " )
cs$term = str_replace( cs$term, "model", "model " )
table( cs$term )

cs <- cs %>%
  dplyr::filter( term != "(Intercept)" ) %>%
  mutate( queen = ifelse( str_detect( term, "Q " ), "queen",
                          ifelse( str_detect( term, "model" ), "model", "coef" ) ),
          term = str_replace(term, "model |queen ", "" ) )

csA = cs

c_coef <- filter( csA,
                  term %in% c( "N5000", "cov_medium", "cov_large", "home", "(Intercept)" ) ) %>%
  arrange( term ) %>%
  dplyr::select( -queen ) %>%
  relocate( term )


cs <- cs %>%
  dplyr::filter( !term %in% c( "N5000", "cov_medium", "cov_large", "home", "(Intercept)" ) )
table( cs$term )

# Sort the coefficients by performance in terms of rmse
ord = cs %>% 
  dplyr::filter( measure =="rmse" ) %>%
  mutate( f = reorder( factor( term ), estimate ) )
ord$f

cs
cs <- mutate( cs, 
              term = factor( term, levels = levels(ord$f) ) )
cs

levels( cs$term[ cs$queen == "queen" ] )


## Make the final coefficient plots ----


# Plot model and queen on single plot
library( scales )
```

# coef_plot.pdf

```{r coef_plot.pdf}
ggplot( cs, aes( term, estimate, color = measure ) ) +
  facet_wrap( ~ queen, scales = "free" ) +
  geom_hline( yintercept = 0 ) +
  #  geom_linerange( aes( ymin = 0, ymax = estimate ),
  #                  position = position_dodge(width = 0.3),
  #                  size = 1, alpha=0.5) +
  geom_point( position = position_dodge(width = 0.4) ) +
  geom_errorbar( aes( ymin = estimate - 2*std.error, ymax = estimate + 2*std.error ),
                 position = position_dodge(width = 0.4), 
                 width = 0 ) +
  coord_flip() +
  theme_minimal() +
  labs( x = "", y="" ) +
  scale_x_discrete( labels = label_wrap(10) )

##ggsave( filename = "graphs/sree2024/coef_plot.pdf", width = 11, height = 6 )



# Plot the model coefficients only

cs$termW = cs$term
lvl = levels( cs$termW )
levels( cs$termW ) <- str_pad(lvl, 
                              width = max(nchar(lvl)), 
                              side = "left")


c2 <- filter( cs, queen != "queen" )

```

# coef_plot.pdf 2

```{r coef_plot.pdf 2}
ggplot( c2, aes( term, estimate, color = measure ) ) +
  geom_hline( yintercept = 0 ) +
  geom_point( position = position_dodge(width = 0.4) ) +
  geom_errorbar( aes( ymin = estimate - 2*std.error, ymax = estimate + 2*std.error ),
                 position = position_dodge(width = 0.4), 
                 width = 0 ) +
  coord_flip() +
  theme_minimal() +
  labs( x = "", y="" )  +
  scale_y_continuous( limits = c( -1, 1)) +
  theme( plot.margin = unit(c(1, 0.1, 0.1, 1.5), "cm") ) +
  scale_x_discrete( labels = label_wrap(10) )

#ggsave( filename = "graphs/sree2024/coef_plot.pdf",
 #       width = 7, height = 6 ) 


# Plot the queens only

# TODO: I don't like the shift relative to ATE.  Hard to see variation
# in the rmse across queens.  Is this ideal?

```

# coef_plot_queen.pdf

```{r coef_plot_queen.pdf}
c3 = filter( cs, queen == "queen" )
ggplot( c3, aes( term, estimate, color = measure ) ) +
  geom_hline( yintercept = 0 ) +
  geom_point( position = position_dodge(width = 0.4) ) +
  geom_errorbar( aes( ymin = estimate - 2*std.error, ymax = estimate + 2*std.error ),
                 position = position_dodge(width = 0.4), 
                 width = 0 ) +
  coord_flip() +
  theme_minimal() +
  labs( x = "", y="" )  +
  scale_y_continuous( limits = c( -1, 1)) +
  theme( plot.margin = unit(c(1, 0.1, 0.1, 1.5), "cm") ) +
  scale_x_discrete( labels = label_wrap(10) )

#ggsave( filename = "graphs/sree2024/coef_plot_queen.pdf",
 #       width = 7, height = 6 ) 


```

# ex_factor_plot.pdf

```{r ex_factor_plot.pdf}
# Plot simulation factors only
ggplot( c_coef, aes( term, estimate, color = measure ) ) +
  geom_hline( yintercept = 0 ) +
  geom_point( position = position_dodge(width = 0.4) ) +
  geom_errorbar( aes( ymin = estimate - 2*std.error, ymax = estimate + 2*std.error ),
                 position = position_dodge(width = 0.4), 
                 width = 0 ) +
  coord_flip( clip="on") +
  theme_minimal() +
  labs( x = "", y="" ) +
  scale_y_continuous( limits = c( -1, 1)) +
  theme( plot.margin = unit(c(1, 0.1, 0.1, 1.5), "cm") ) +
  scale_x_discrete( labels = label_wrap(10) )




#ggsave( filename = "graphs/sree2024/ex_factor_plot.pdf", 
 #       width = 7, height = 6 ) 


```

# Plot everything on single plot

```{r Plot everything on single plot}
# Fix the ordering of factors to keep grouping

csA$term <- fct_reorder( factor( csA$term ), 
                         100 * as.numeric( as.factor( csA$queen ) ) + (csA$measure =="rmse") * csA$estimate )
levels( csA$term )
ggplot( csA, aes( term, estimate, color = measure ) ) +
  geom_hline( yintercept = 0 ) +
  geom_point( position = position_dodge(width = 0.4) ) +
  geom_errorbar( aes( ymin = estimate - 2*std.error, ymax = estimate + 2*std.error ),
                 position = position_dodge(width = 0.4), 
                 width = 0 ) +
  coord_flip( clip="on") +
  theme_minimal() +
  labs( x = "", y="" ) +
  scale_y_continuous( limits = c( -1, 1)) +
  theme( plot.margin = unit(c(1, 0.1, 0.1, 1.5), "cm") ) +
  scale_x_discrete( labels = label_wrap(10) )


