---
title: "12 - expore effects - ASAP"
author: "Selby"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(here)

# Styler
library(styler)
library(lintr)

# Load previous programs
source(here::here("R/packages.R"))
```

# Load Data from Previous File

```{r}
source(here::here("treatment_effects/21-Calculate CATES_ca.R"))

```

# Review Files

```{r}
cat("Continuous outcome Variable - ", y_cont, "\n")
cat("Binary outcome Variable - ", y_binary, "\n")
cat("Treatment Variable - ", treatment, "\n")
cat("Covariates - ", cv, "\n")

dat <- dat_ca
```

# Step 1: Establish Heterogeneity

## Calculate Rank & Z-score for each outcome
```{r}
sd_cont <- sd(dat$cate_cont, na.rm = TRUE)
mean_cont <- mean(dat$cate_cont, na.rm = TRUE)

sd_binary <- sd(dat$cate_binary, na.rm = TRUE)
mean_binary <- mean(dat$cate_binary, na.rm = TRUE)

dat <- dat %>%
  mutate(cate_cont_z = (cate_cont - mean_cont)/sd_cont,
         cate_cont_rank =rank(cate_cont),
         cate_binary_z = (cate_binary - mean_binary)/sd_binary,
         cate_binary_rank =rank(cate_binary))
```
## Test for Heterogenity {.tabset}



1. Regress CATE against rank/Z-score
2. Plot Cate and rank/Z-score


### Binary Variable

#### Rank
```{r}
bin_fit <- lm(cate_binary ~ cate_binary_rank, data = dat)
summary(bin_fit)

dat %>%
  ggplot(aes(x = cate_binary_rank, y = cate_binary) ) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE)
```

#### Z-Score
```{r}
bin_fit <- lm(cate_binary ~ cate_binary_z, data = dat)
fit_sum <- summary(bin_fit)

f <- 3
fit_sum$coefficients <- round(fit_sum$coefficients, f)
fit_sum$residuals <- round(fit_sum$residuals, f)
fit_sum$cov.unscaled <- round(fit_sum$cov.unscaled, f)

dat %>%
  ggplot(aes(x = cate_binary_z, y = cate_binary) ) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE)
```

### Continuous Variable

#### Rank
```{r}
cont_fit <- lm(cate_cont ~ cate_cont_rank, data = dat)
summary(cont_fit)

dat %>%
  ggplot(aes(x = cate_cont_rank, y = cate_cont) ) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE)
```

#### Z-Score
```{r}
cont_fit <- lm(cate_cont ~ cate_cont_z, data = dat)
fit_sum <- summary(cont_fit)


fit_sum$coefficients <- round(fit_sum$coefficients, f)
fit_sum$residuals <- round(fit_sum$residuals, f)
fit_sum$cov.unscaled <- round(fit_sum$cov.unscaled, f)

dat %>%
  ggplot(aes(x = cate_cont_z, y = cate_cont) ) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE)
```

# Step 2: Best Linear Predictor {.tabset}

## Binary

### Fit Random Forest on CATES
```{r}

n_var = 10 #number of Important Variables

#Set Formula
x_vars <- stringr::str_c(cv, collapse = "+")
formula <- paste0("cate_binary~", x_vars)
formula <- as.formula(formula)

# Randomforest for variable importance
rf_model <- randomForest(formula, data=dat, importance=TRUE, ntree=500)

#Variable Importance plot
# Shows 10 most important variables
varImpPlot(rf_model, n.var = n_var)

# Find most important variables
importance <- rf_model %>% 
  importance() %>%
  data.frame() %>% 
  arrange(desc(X.IncMSE))

# Selects top n_var
top_variables <- importance %>% 
  top_n(n_var, X.IncMSE)
top_variables_names <- rownames(top_variables)
# 
# # create Dataframe with top variables
# top_vars_df <- top_variables_names %>%
#   data.frame() %>%
#   mutate(var_type = case_when(
#     TRUE ~ "continuous",
#     str_detect(`.`, "_99") ~ "missing",
#     str_detect(`.`, "_\\d+$") ~ "categorical"
#     )
#   )
# 
# colnames(top_vars_df)[1] <- "variable"
# 
# # Output Variable importance table
# cap_text <- paste("Top", n_var, "Most important variables for predicting CATE on", y_binary, sep = " ")
# 
# top_vars_df %>% 
#     knitr::kable(caption = cap_text)
```

### Regress CATE on Best Predictors
```{r}
x_vars <- stringr::str_c(top_variables_names, collapse = "+")
formula <- paste0("cate_binary~", x_vars)
formula <- as.formula(formula)

lm_fit_b <- lm(formula, data = dat)
summary(lm_fit_b)

```

## Continuous

### Fit Random Forest on CATES
```{r}

n_var = 10 #number of Important Variables

#Set Formula
x_vars <- stringr::str_c(cv, collapse = "+")
formula <- paste0("cate_cont~", x_vars)
formula <- as.formula(formula)

# Randomforest for variable importance
rf_model <- randomForest(formula, data=dat, importance=TRUE, ntree=500)

#Variable Importance plot
# Shows 10 most important variables
varImpPlot(rf_model, n.var = n_var)

# Find most important variables
importance <- rf_model %>% 
  importance() %>%
  data.frame() %>% 
  arrange(desc(X.IncMSE))

# Selects top n_var
top_variables <- importance %>% 
  top_n(n_var, X.IncMSE)
top_variables_names <- rownames(top_variables)
# 
# # create Dataframe with top variables
# top_vars_df <- top_variables_names %>%
#   data.frame() %>%
#   mutate(var_type = case_when(
#     TRUE ~ "continuous",
#     str_detect(`.`, "_99") ~ "missing",
#     str_detect(`.`, "_\\d+$") ~ "categorical"
#     )
#   )
# 
# colnames(top_vars_df)[1] <- "variable"
# 
# # Output Variable importance table
# cap_text <- paste("Top", n_var, "Most important variables for predicting CATE on", y_cont, sep = " ")
# 
# top_vars_df %>% 
#     knitr::kable(caption = cap_text)
```

### Regress CATE on Best Predictors
```{r}
x_vars <- stringr::str_c(top_variables_names, collapse = "+")
formula <- paste0("cate_cont~", x_vars)
formula <- as.formula(formula)

lm_fit_c <- lm(formula, data = dat)
summary(lm_fit_c)

```

# Step 3: Quantile Personas

## Identify CATE Quantiles

```{r}
quant_binary <- quantile(dat$cate_binary, probs = seq(0, 1, 0.25))
quant_cont <- quantile(dat$cate_cont, probs = seq(0, 1, 0.25))

dat <- dat %>%
  mutate(quant_b = cut(cate_binary, breaks = quant_binary, labels = FALSE, include.lowest = TRUE),
         quant_c = cut(cate_cont, breaks = quant_cont, labels = FALSE, include.lowest = TRUE))

```

## Demographic Variables
```{r}
gender <- "FEMALE"
age <- "AGE"
#employed <- "BLWORK"
parent <- "ONEPARNT"
```

## Personal Tables{.tabset}

### Binary

```{r}
tab_binary <- dat %>%
  group_by(quant_b) %>%
  summarize(FEMALE = mean(FEMALE, na.rm = TRUE),
            AGE = mean(AGE, na.rm = TRUE),
            #BLWORK = mean(BLWORK, na.rm = TRUE),
            ONEPARNT = mean(!!sym(parent), na.rm = TRUE)
            )

overall_b  <- dat %>%
  summarize(
    quant_b = "Overall",
   FEMALE = mean(FEMALE, na.rm = TRUE),
            AGE = mean(AGE, na.rm = TRUE),
            #BLWORK = mean(BLWORK, na.rm = TRUE),
            ONEPARNT = mean(!!sym(parent), na.rm = TRUE)
            )

tab_binary <- rbind(overall_b, tab_binary)
knitr::kable(tab_binary)
```


### Continuous

```{r}
tab_cont <- dat %>%
  group_by(quant_c) %>%
  summarize(FEMALE = mean(FEMALE, na.rm = TRUE),
            AGE = mean(AGE, na.rm = TRUE),
            #BLWORK = mean(BLWORK, na.rm = TRUE),
            ONEPARNT = mean(!!sym(parent), na.rm = TRUE)
            )
            

overall_c  <- dat %>%
  summarize(
    quant_c = "Overall",
    FEMALE = mean(FEMALE, na.rm = TRUE),
            AGE = mean(AGE, na.rm = TRUE),
            #BLWORK = mean(BLWORK, na.rm = TRUE),
            ONEPARNT = mean(!!sym(parent), na.rm = TRUE)
            )

tab_cont <- rbind(overall_c, tab_cont)
knitr::kable(tab_cont)
```

