---
title: "Untitled"
author: "David Selby"
date: "2024-04-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
library(rlang)
library(ggExtra)
library(kableExtra)
library(knitr)

# Styler
library(styler)
library(lintr)

# Load previous programs
source(here::here("R/setup.R"))
source(here::here("simulation/00_add_treatment_effects.R"))
source(here::here("methods/cf_model.R"))
source(here::here("ASAP/01_load_real_ASAP.R"))
source(here::here("CA/01_load_real_CA.R"))
source(here::here("treatment_effects/treatment_effects_scripts/setup_te.R"))


```

```{r data prep}
## CA
dat <- ca_subset_imputed

# Assign names of Covariates
co_vars <- ca_covariates
outcome_vars <- ca_outcomes
treatment_vars <- ca_treatment
te_vars <- paste0("te_", outcome_vars)
## ASAP

# dat <- asap_subset_imputed
#
# # Assign names of Covariates
# co_vars <- asap_covariates
# outcome_vars <- asap_outcomes
# treatment_vars <- asap_treatment

# Complete Cases for outcomes
dat <- dat %>% filter(complete.cases(.))

# Seperate data frame into covariates, outcomes, and treatment variables

x_tr <- dat %>%
  select(all_of(co_vars))

# Convert all factor variables in covariate data frame to dummy variables
x_tr <- dummy_cols(x_tr, remove_selected_columns = TRUE) %>% as.matrix()

y_tr <- dat %>%
  select(all_of(outcome_vars))  %>%
  as.matrix

d_tr <- dat %>%
  select(all_of(treatment_vars)) %>%
  as.matrix

# NOTE THIS treats the training set the same as the test data set. May need to update with different subset
x_val <- x_tr 

ntrain <- nrow(x_tr)

dat_te <- dat

```

## Causal Forest

# Calculate Treatment effects
```{r}

#Specify ml_method in this case cf_model for causal forest

te_cf <- calculate_te( x_tr, y_tr, d_tr, x_val, ntrain, ml_method = cf_model)

#combine data frame with treatment effects

dat_te <- cbind(dat_te, te_cf)

```


# Regression on Outcome

```{r}
# This code runs a regression each of the outcome variables of the treatment and specified covariates.

#create empty list
reg_model <- list()

# String vector of outomes names
outcomes_names <- colnames(y_tr)

#combine treatment and covariate
temp_dat <- cbind(d_tr, x_tr) %>% 
  data.frame()

# Fit lm for each outcome variable
for (i in 1:ncol(y_tr)){
  lm_fit <- lm(y_tr[, i] ~ . , data = temp_dat )
  reg_model[[i]] <- summary(lm_fit)
}

#Rename list model variables
reg_model <- setNames(reg_model, outcomes_names)

#Check reg_model results
reg_model$Y18JBERNA_06
```

# Extra Regression Results
```{r}
#For Paramaterization later
j = 1 # Which Dependent variable

lm_model <- reg_model[[j]]
lm_ate <- lm_model$coefficients[treatment_vars,]

# Reformat treatment effects variable to data frame and snake case
lm_ate <- lm_ate %>%
  data.frame() %>%
  t() %>%
  data.frame()

colnames(lm_ate) <- colnames(lm_ate) %>% snakecase::to_snake_case()

# Add Confidence interval and Signficnance at 95%
lm_ate <- lm_ate %>%
  mutate(
    lower_ci = estimate - (std_error * 1.96),
    upper_ci = estimate + (std_error * 1.96),
    significant = ifelse(pr_t <= 0.05, 1, 0)
  )

# ate for plots and graphs:
lm_mean <- lm_ate$estimate
lm_lower_ci <- lm_ate$lower_ci
lm_upper_ci <- lm_ate$upper_ci


```


# Variable Importance

```{r}
# @TODO - Check instability in outcome variables.
# Construct variable importance plots and tables for each treatment effect variable

#For Paramaterization later
i = 1 # Which Variable
n_var = 10 #number of Important Variables

# Set tau - treatment effects
tau <- te_cf[,i]

# Randomforest for variable importance
rf_model <- randomForest(tau ~ ., data=x_tr, importance=TRUE, ntree=500)

#Variable Importance plot
# Shows 10 most important variables
varImpPlot(rf_model, n.var = n_var)

# Find most important variables
importance <- rf_model %>% 
  importance() %>%
  data.frame() %>% 
  arrange(desc(X.IncMSE))

# Selects top n_var
top_variables <- importance %>% 
  top_n(n_var, X.IncMSE)
top_variables_names <- rownames(top_variables)

# create Dataframe with top variables
top_vars_df <- top_variables_names %>%
  data.frame() %>%
  mutate(var_type = case_when(
    str_detect(`.`, "_99") ~ "missing",
    str_detect(`.`, "_\\d+$") ~ "categorical",
    TRUE ~ "continuous")
  )

colnames(top_vars_df)[i] <- "variable"

# Output Variable importance table
cap_text <- paste("Top", n_var, "Most important variables for predicting IATE on", outcomes_names[i], sep = " ")

top_vars_df %>% 
    knitr::kable(caption = cap_text)

#Run x times.  Save dataframe.
```

# Dynamic Model IATE for  `r outcomes_names[i]` on top `r n_var` most important variables

```{r}
# The dynamic mode will regress the 10 most important variables from the random forest variable importance onto the treatment effects variable.

# Sets up data for dynamic model
temp_x <- x_tr[, top_variables_names] %>%
  data.frame()

# fit dynamic model using lm
dynamic_model <- lm(tau ~ ., data = temp_x)

#Return results of dynamic model.
summary(dynamic_model)


```
# Covariate Drill down

## Binary Covariate
```{r}
# Function for checking if continous variable is binary
is_binary <- function(x) {
  unique_values <- unique(x)
  all(unique_values %in% c(0, 1)) && length(unique_values) <= 2
}

# Select only Continuous variables
continuous_var <- top_vars_df %>% 
  filter(var_type == "continuous")


#Filter temp table to just continous variables
#used for checking if columns contain binary variables
binary_var_check <- temp_x %>%
  mutate_all(as.numeric) %>%
  select(all_of(continuous_var[,1]))

# For loop to check each variable in binary_var_check
# And convert them to binary in continuous_var
for( i in 1:ncol(binary_var_check)){
  col <- colnames(binary_var_check)[i]
  if(is_binary(binary_var_check[,col])){
    continuous_var$var_type[i] <- "binary"
  }
}

# Combine continuous_var with top_vars_df
# Binary Variables updated
top_vars_df[top_vars_df$var_type == "continuous",] <- continuous_var



```


# Binary Covariate Plot

```{r}

# Select binary Variables
binary_var <- top_vars_df %>% 
  filter(var_type == "binary")

#For Paramaterization later
i = 1

#Selected 1 variable
x_var <- binary_var[i,1]

# Create Temp Data
temp_dat <- cbind(tau, temp_x)

#Histogram
temp_dat %>%
  mutate(group := factor(!!sym(x_var))) %>%
  ggplot(aes(x = tau, fill = group)) + 
  geom_histogram(colour = "grey40", alpha = 0.5, position = "identity") +
  geom_vline(xintercept = mean(tau), color = "black", linetype = "solid", size = 1) +
  geom_vline(xintercept = lm_mean, color = "firebrick", linetype = "longdash", size = 1) +
  geom_vline(xintercept = lm_lower_ci, color = "firebrick2", linetype = "dotted", size = 1) +
  geom_vline(xintercept = lm_upper_ci, color = "firebrick2", linetype = "dotted", size = 1) +
  geom_vline(xintercept = 0, color = "gray10", size = .5) +
  geom_hline(yintercept = 0, color = "gray10", size = .5)
```

## Binary Table
```{r}
tab_binary <- temp_dat %>%
  group_by(!!sym(x_var)) %>%
  summarize(mean_te = mean(tau),
            sd_te = sd(tau))

var_name <- colnames(tab_binary)[1]

tab_binary <- tab_binary %>%
  mutate(!!sym(x_var) := paste(var_name, !!sym(x_var), sep = "_"))

colnames(tab_binary)[1] <- "Group"

tab_overall <- data.frame(
  Group = "Tau", 
  mean_te = mean(tau), 
  sd_te = sd(tau))

tab_lm <-data.frame(
  Group = "linear model",
  mean_te = lm_ate$estimate,
  sd_te = lm_ate$std_error
)

tab <- rbind(tab_overall,
             tab_lm,
             tab_binary)

tab %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
             
```

## Continuous Covariate

```{r}
#For Paramaterization later
i = 1 # Which Variable

continuous_var <- top_vars_df %>% 
  filter(var_type == "continuous")

x_var <- continuous_var[i,1]

temp_dat <- cbind(tau, temp_x) %>%
  mutate_all(as.numeric)

# Plot continuous Variable
p <- temp_dat %>%
  ggplot(aes(y = tau, x = (!!sym(x_var)))) +
  # Add the scatter plot points
  geom_point() + 
  # Add a linear model line with a 95% confidence interval 
  geom_smooth(method = "lm", level = 0.95) + 
  # Set x-axis limits based on min and max of x variable 
  scale_x_continuous(limits = c(min(temp_dat[x_var], na.rm = TRUE), max(temp_dat[x_var], na.rm = TRUE))) 

  
ggExtra::ggMarginal(p, type = "histogram")
```




# Catagorical Covariate

## Factor to Condence Dummies
```{r}
# Create a function to condense dummy variables
condense_dummies <- function(df, prefix) {
  df = dat_con
  prefix = paste0(org_name, "_")
  # Create an empty vector to store the results
  result <- vector("numeric", nrow(df))
  # Iterate over each row
  for (i in 1:nrow(df)) {
    # Find which dummy variable is 1 and assign the corresponding value
    for (j in 1:length(prefix)) {
      if (df[i, paste0(prefix, j)] == 1) {
        result[i] <- j
        break
      }
    }
  }
  
  # Return the result as a factor
  return(factor(result))
}

```

```{r}
categorical_var <- top_vars_df %>% 
  filter(var_type == "categorical")

#For Parameterization, Later
i = i
var_name <-categorical_var[i, 1]

#First we need to get the rest of the categorical variable from the main dataset
org_name <- str_replace(var_name, "_\\d+$", "")

#Condensed table for dummy variables
#Look up Variable from original dataset
dat_con <- dat %>%
  data.frame %>%
  select(contains(org_name))

dat_con <- cbind(tau, dat_con)

#Histogram
dat_con %>%
  mutate(group := factor(!!sym(org_name))) %>%
  ggplot(aes(x = tau, fill = group)) + 
  geom_histogram(colour = "grey40", alpha = 0.25, position = "identity") +
  geom_vline(xintercept = mean(tau), color = "black", linetype = "solid", size = 1) +
  geom_vline(xintercept = lm_mean, color = "firebrick", linetype = "longdash", size = 1) +
  geom_vline(xintercept = lm_lower_ci, color = "firebrick2", linetype = "dotted", size = 1) +
  geom_vline(xintercept = lm_upper_ci, color = "firebrick2", linetype = "dotted", size = 1) +
  geom_vline(xintercept = 0, color = "gray10", size = .5) +
  geom_hline(yintercept = 0, color = "gray10", size = .5) +
  scale_alpha_manual(values = c(var_name = 1)) + 
  theme_minimal() +
  guides(alpha = FALSE) #remove Alpha Legend

#boxplot
dat_con %>%
  mutate(group := factor(!!sym(org_name))) %>%
  ggplot(aes(x = tau, fill = group)) + 
  geom_boxplot(colour = "grey40", alpha = 0.25) +
  geom_vline(xintercept = mean(tau), color = "black", linetype = "solid", size = 1) +
  geom_vline(xintercept = lm_mean, color = "firebrick", linetype = "longdash", size = 1) +
  geom_vline(xintercept = lm_lower_ci, color = "firebrick2", linetype = "dotted", size = 1) +
  geom_vline(xintercept = lm_upper_ci, color = "firebrick2", linetype = "dotted", size = 1) +
  geom_vline(xintercept = 0, color = "gray10", size = .5) +
  geom_hline(yintercept = 0, color = "gray10", size = .5) +
  theme_minimal()
  

```

@TODO: Need to add multiple IATE methods. Currently only Causal Forest.
\newline
@TODO: Need to add comparison between algorithims
